PANCHANGE_analysis

### 2020-09-22 PANCHANGE_analysis.Rmd
updated the exclusion chunk in the exclusion_descriptives script

```{r gad percentage plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r gad percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

```{r gad plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nRetrospective vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic"))
```

@@

```{r gad percentage plot retro_prepan sum}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
 #   labels = c("Baseline", "Prepandemic", "Retrospective")
    )
```

```{r gad percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
#    labels = c("Prepandemic", "Retrospective")
    ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq percentage plot retro_prepan}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r phq plot retro_prepan diff}
dat.long.phq.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

```{r phq percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq percentage plot retro_prepan sum}
dat.long.phq.sum %>%
  #  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PHQ9 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  )
```

```{r phq percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.phq.sum %>%
  #  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PHQ9 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir percentage plot retro_prepan}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r ocir plot retro_prepan diff}
dat.long.ocir.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

```{r ocir percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir percentage plot retro_prepan sum}
dat.long.ocir.sum %>%
  ggplot(mapping = aes(
    x = ocir.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "OCI-R scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  )
```

```{r ocir percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.ocir.sum %>%
  ggplot(mapping = aes(
    x = ocir.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "OCI-R score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r pcl percentage plot retro_prepan sum}
dat.long.pcl.sum %>%
  ggplot(mapping = aes(
    x = pcl.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PCL scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  )
```

```{r pcl percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.pcl.sum %>%
  ggplot(mapping = aes(
    x = pcl.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PCL score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

# Create additional datasets for analyses
Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:

@@

```{r model0b function}
model0b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model0b_estimates"),
         tidy(get(paste0(outcome,".model0b")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
               "depressive_disordersDepressive disorder" = "Depressive disorders",
               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
               "eating_disordersEating disorder" = "Eating disorders",
               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
               "mhd.personality_disorderPersonality disorder" = "Personality disorder"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

```{r model0b.explan function}
model0b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var, 
                             "anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

>>>>

```{r gad percentage plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic", "Retrospective"))
```

```{r gad percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

```{r gad plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nRetrospective vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic"))
```

@@

```{r gad percentage plot retro_prepan sum}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    )
```

```{r gad percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq percentage plot retro_prepan}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic", "Retrospective"))
```

```{r phq plot retro_prepan diff}
dat.long.phq.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Retrospective"))
```

```{r phq percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic", "Retrospective")
    ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r phq percentage plot retro_prepan sum}
dat.long.phq.sum %>%
  #  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PHQ9 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
  )
```

```{r phq percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.phq.sum %>%
  #  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PHQ9 score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir percentage plot retro_prepan}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic", "Retrospective"))
```

```{r ocir plot retro_prepan diff}
dat.long.ocir.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Retrospective"))
```

```{r ocir percentage plot retro_prepan resized, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(
    values = palette,
    labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir percentage plot retro_prepan sum}
dat.long.ocir.sum %>%
  ggplot(mapping = aes(
    x = ocir.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "OCI-R scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
  )
```

```{r ocir percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.ocir.sum %>%
  ggplot(mapping = aes(
    x = ocir.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "OCI-R score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r pcl percentage plot retro_prepan sum}
dat.long.pcl.sum %>%
  ggplot(mapping = aes(
    x = pcl.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PCL scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
  )
```

```{r pcl percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
dat.long.pcl.sum %>%
  ggplot(mapping = aes(
    x = pcl.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "PCL score",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
  ) +
  facet_wrap("Disorder_hierarchical")
```

# Create subsets of data for analyses
Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:

@@

```{r model0b function}
model0b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model0b_estimates"),
         tidy(get(paste0(outcome,".model0b")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
               "depressive_disordersDepressive disorder" = "Depressive disorders",
               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
               "eating_disordersEating disorder" = "Eating disorders",
               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
               "mhd.personality_disorderPersonality disorder" = "Personality disorder"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

```{r model0b.explan function}
model0b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var, 
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
